Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-22 paper.qmd
Updated Figure 14 a2, b2

@@

pbmc_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("a2")

@@

pbmc_proj_umap_model1_best <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c") +
  geom_point(
    size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("b2")

>>>>

axes_obj <- gen_axes(
  proj = projection,
  limits = 1,
  axis_pos_x = -0.4,
  axis_pos_y = -0.4,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.057)

@@

pbmc_proj_umap_model1 <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c",
    linewidth = 1) +
  geom_point(
    #size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, 1)) +
  ylim(c(-0.6, 1)) +
  interior_annotation("a2")

@@

pbmc_proj_umap_model1_best <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c",
    linewidth = 1) +
  geom_point(
    #size = 0.5,
    alpha = 0.2) +
  scale_color_manual(values = c("#000000", "#33a02c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.6, 1)) +
  ylim(c(-0.6, 1)) +
  interior_annotation("b2")
